%-------------------------
% Resume in Latex
% Author : Aamogh Sawant
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{fontspec}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.25in}

\setmainfont{Times New Roman}

% Section title format
\titleformat{\section}{
  \scshape\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r} \textbf{#1} & #2 \\ \textit{\small#3} & \textit{\small #4} \end{tabular*}\vspace{-5pt}}
\newcommand{\resumeSubSubheading}[2]{\item \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r} \textit{\small#1} & \textit{\small#2} \end{tabular*}\vspace{-5pt}}
\newcommand{\resumeProjectHeading}[2]{\item \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r} \small#1 & #2 \end{tabular*}\vspace{-5pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Aamogh Sawant} \\ \vspace{1pt}
    \small \href{mailto:aamoghsawantt@gmail.com}{aamoghsawantt@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/aamogh-sawant-229482278/}{\underline{linkedin.com/in/aamogh-sawant}} $|$ 
    \href{https://github.com/aamoghS}{\underline{github.com/aamoghS}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Central Florida - College of Engineering}{Orlando, FL}
      {B.S. in Computer Science (Expected)}{May 2027}
    \resumeItemListStart
      \resumeItem{Relevant Coursework: IB Computer Science, Intro to C, Discrete Math, Multivariable Calculus}
      \resumeItem{Certifications: Java and Python Microsoft Certification, CompTIA IT Certification}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Black and Gold Analytics}{Orlando, FL}
      {Workshop Director and Competition Coordinator}{September 2024-Present}
      \resumeItemListStart
             \resumeItem{Organized 5+ workshops on data analytics and web development, directly training 100+ participants in hands-on projects.}
            \resumeItem{Coordinated 3+ competitions with 50+ participants each, resulting in innovative analytics projects and strengthened teamwork.}
      \resumeItemListEnd



    \resumeSubheading
      {Kumon}{Jacksonville, FL}
      {Center Assistant}{August 2020 -- May 2024}
      \resumeItemListStart
        \resumeItem{Monitored students' progress by inputting scores from Kumon homework into the CMS (Kumon Database) system, which assigned further work based on achieved scores.}
        \resumeItem{Tutored over 20 students in advanced math and grammar, leading to a 30\% improvement in test scores over 6 months.}

      \resumeItemListEnd

    \resumeSubheading
      {First Robotics}{Jacksonville, FL}
      {Team Resistance Programmer}{August 2022 -- April 2024}
      \resumeItemListStart
        \resumeItem{Utilized Java to develop software for an industrial-sized robot for field-based tasks and competitions.}
        \resumeItem{Collaborated with teammates to build and program components, engaging with executive coaches to foster mechanical innovation.}
      \resumeItemListEnd

    \resumeSubheading
      {NLP Logix}{Jacksonville, FL}
      {Data Science and Machine Learning Intern}{June 2023 -- August 2023}
      \resumeItemListStart
        \resumeItem{Used Tableau to identify trends within data and establish relationships through interactive dashboards.}
        \resumeItem{Developed a machine learning algorithm in Python using Random Forest Classifier learning models to create a predictive model for play type based on analytic parameters.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{KnightHacks} $|$ \emph{Next.js, Node.js, MongoDB}}{September 2024}
      \resumeItemListStart
        \resumeItem{Developed a web application using JavaScript and Next.js to educate homeowners on power consumption across Florida counties, incorporating interactive features via a Pigeon Maps integration.}
        \resumeItem{Implemented a MongoDB backend to efficiently store and query county data, facilitating real-time updates through a custom API that responds to user interactions with the map markers.}
      \resumeItemListEnd

        \resumeProjectHeading
      {\textbf{ShellHacks 2024} $|$ \emph{Typescript, Javascript, Google Api}}{September 2024}
      \resumeItemListStart
        \resumeItem{Developed an AR interface for daily-use features like reminders, weather updates, and music, using Snapchat Spectacles, JavaScript, and TypeScript.}
        \resumeItem{Collaborated with a team to quickly adapt to new technologies and optimize project workflow despite time constraints.}
      \resumeItemListEnd


    \resumeProjectHeading
      {\textbf{Olympic Medal Counter} $|$ \emph{Python, BeautifulSoup, Matplotlib}}{March 2023}
      \resumeItemListStart
        \resumeItem{Programmed an application with Python and BeautifulSoup to extract medal counts from BBC's website and generate a dictionary of countries with medal data.}
        \resumeItem{Created data visualizations using Matplotlib and Pandas to display and rank countries based on medal counts.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Music Analyzer} $|$ \emph{Python, Spotify API, Pandas}}{June 2023}
      \resumeItemListStart
        \resumeItem{Developed an application with Python and Spotify Web API to extract track features and generate optimal playlists based on user preferences.}
        \resumeItem{Built an algorithm to display song pairings based on metadata such as genre and song signatures to create rankings.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Java, Python, C/C++, SQL, JavaScript, HTML/CSS, Swift} \\
      \textbf{Technologies}{: Visual Studio, JetBrains IDEs, Jupyter Notebooks, Tableau} \\
      \textbf{Libraries}{: TesnorFlow, Pandas, Matplotlib, BeautifulSoup, NumPy} \\
      \textbf{Tools}{: Git, GitHub, LaTeX, Windows}
    }
  \resumeSubHeadingListEnd

%-----------ASSOCIATIONS-----------

\end{document}
